Title

### 2023-09-23 paper/paper.tex
paper

\subsection{Represent protein sequences as continuous vectors}
short description of the main characteristics of each embedder 
\subsubsection{SeqVec}

\subsection{Combining the (contextual) representations}
We tried four methods to join togheter the amminoacid embeddings in order to produce a fixed size embedding for the chunk: average, maximum, sum and principal component analysis (PCA).

@@

\onecolumn
\begin{table}[htb]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length (chunk) & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64 per chunk   \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768 per chunk \\
    prose   \cite{bepler2021learning}                   & 512   & 100 per amino acid   \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 per ammino acid\\
    evolutionary scale modeling (esm2) \cite{lin2022language}   & 1024    & 1280 per ammino acid \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments, their maximum imput length and the dimension of the embedding produced.}
\label{tab:embedders}
\end{table}
\twocolumn

>>>>

\subsection{Represent protein sequences as continuous vectors}
short description of the main characteristics of each embedder

\subsubsection{prose}
learning with strictural supervision

\subsubsection{alphafold}

- is a deep learning system not a language model

- predict residue-residue distances from sequence families and fold proteins based on the predicted distance constraints

- rely on large datasets of protein sequences that are similar enough to be aligned with high confidence but contain enough divergence to confidently infer statistical couplings between positions

- unable to learn patterns across large-scale databases of possibly unrelated proteins and have limited ability to draw on the increasing structure and function information available

\subsubsection{SeqVec}
To build their model Heinzinger et al.\cite{heinzinger2019modeling} adapted the standar ELMo configuration \cite{peters-etal-2018-deep} to work with protein sequences modifying the number of tokens and the unroll steps. It is composed by 1 CharCNN and 2 LSTM-Layers. Given a protein sequence of arbitrary length it returns 3072 features for each residue derived by concatenating the outputs of the three layers of ELMo, each describing a token with a vector of length 1024. In order to obtain a smaller representation for each amminoacid i computed the mean of the three layers (as also suggested in the official repository). Given the architecture of the ELMo, these representation are contextual-dependent.

\subsection{Combining the (contextual) representations}derived by concatenating the outputs of the three layers of ELMo, each describing a token with a vector of length 1024
We tried four methods to join togheter the amminoacid embeddings in order to produce a fixed size embedding for the chunk: average, maximum, sum and principal component analysis (PCA).

@@

\onecolumn
\begin{table}[htb]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length (chunk) & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64 per chunk   \\
    seqvec \cite{heinzinger2019modeling} & 1024 & 1024 per amminoacid \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768 per chunk \\
    prose   \cite{bepler2021learning}                   & 512   & 100 per amino acid   \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 per ammino acid\\
    evolutionary scale modeling (esm2) \cite{lin2022language}   & 1024    & 1280 per ammino acid \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments, their maximum imput length and the dimension of the embedding produced.}
\label{tab:embedders}
\end{table}
\twocolumn
